---
title: "Total Sales R Code"
author: "Jorge Fernandez"
date: "2024-05-26"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=TRUE, echo = TRUE, warning = FALSE, message=FALSE)
```
**Loading Libraries**
```{r}
library(ggplot2)
library(ggfortify)
library(janitor)
library(dplyr)
library(lubridate)
library(grid)
library(gridExtra)
library(ggplotify)
library(cowplot)
library(kableExtra)
library(ggpubr)
library(forecast)
library(fBasics)
library(fpp2)
library(zoo)
library(lmtest)
library(tseries)
library(fUnitRoots)
library(astsa) 
library(dynlm) 
library(FinTS)
library(rugarch)
source("eacf.R")
source("Backtest.R")
source("run_stationarity_tests.R")
source("summarize_arima_models.R")
```

## Read In Data
```{r}
retail <- read.csv("train.csv")
```

## Some Initial Cleaning
```{r}
# Clean column names
retail<-clean_names(retail)
colnames(retail)

# Convert date cols to Date format
retail$order_date<-as.Date(retail$order_date,'%d/%m/%Y')
retail$ship_date<-as.Date(retail$ship_date, '%d/%m/%Y')
```

## EDA

**Total Orders and Sales by Category**
```{r}
# Summarize total sales by category
sales_by_category <- retail %>%
  group_by(category) %>%
  summarize(total_sales = sum(sales), .groups = 'drop')

# Summarize total orders by category
orders_by_category <- retail %>%
  group_by(category) %>%
  summarize(total_orders = n(), .groups = 'drop')

# Total Sales by Category
sales_plot <- ggplot(sales_by_category, aes(x = reorder(category, total_sales), y = total_sales, fill = category)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Total Sales by Category", x = NULL, y = "Total Sales") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank())  # Remove x-axis title

# Total Orders by Category
orders_plot <- ggplot(orders_by_category, aes(x = reorder(category, total_orders), y = total_orders, fill = category)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Total Orders by Category", x = NULL, y = "Total Orders") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank())  # Remove x-axis title

# Arrange the plots in a grid
grid.arrange(sales_plot, orders_plot, ncol = 2)

```

```{r}
# Add a log of sales column
retail <- retail %>%
  mutate(log_sales = log(sales))

# Plot for the log of all sales
log_sales_plot <- ggplot(retail, aes(x = log_sales)) +
  geom_density(fill = "lightgray", alpha = 0.5) +
  labs(title = "Density Log(All Sales)", x = "Log of Sales", y = "Density") +
  theme_minimal()

# Plot for the log of sales by category
log_sales_by_category_plot <- ggplot(retail, aes(x = log_sales, fill = category)) +
  geom_density(alpha = 0.5) +
  labs(title = "Density of Log(Sales) by Category", x = "Log of Sales", y = "Density") +
  theme_minimal() +
  theme(legend.position = "right")  

# Arrange the plots in a grid
grid.arrange(log_sales_plot, log_sales_by_category_plot, ncol = 2)
```

```{r}
# Ensure order_date is a Date object
retail$order_date <- as.Date(retail$order_date)

# Aggregate total weekly sales
weekly_sales_total <- retail %>%
  mutate(week_year = as.Date(cut(order_date, "week"))) %>%
  group_by(week_year) %>%
  summarize(total_sales = sum(sales), .groups = 'drop')

# Aggregate weekly sales by category
weekly_sales_category <- retail %>%
  mutate(week_year = as.Date(cut(order_date, "week"))) %>%
  group_by(week_year, category) %>%
  summarize(total_sales = sum(sales), .groups = 'drop')

# Plot for total weekly sales
total_sales_plot <- ggplot(weekly_sales_total, aes(x = week_year, y = total_sales)) +
  geom_line(color = "black", size = 0.5, alpha = 0.8) +
  labs(title = "Total Weekly Sales", x = "Week", y = "Sales") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

# Plot for weekly sales by category
sales_by_category_plot <- ggplot(weekly_sales_category, aes(x = week_year, y = total_sales, color = category)) +
  geom_line(size = 0.5, alpha = 0.8) +
  labs(title = "Weekly Sales by Category", x = "Week", y = "Sales") +
  theme_minimal() +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5)) +
  scale_color_manual(values = c("Furniture" = "firebrick", "Office Supplies" = "seagreen", "Technology" = "steelblue"))

```

```{r}
library(patchwork)

# Combining the plots
plot_layout <- (total_sales_plot / sales_by_category_plot) +
  plot_layout(heights = c(15, 16))  # Adjusting relative heights

plot_layout
```

**Total Sales by Day of Week and Month of Year**
```{r}
# Adding day of the week column
retail <- retail %>%
  mutate(day_of_week = wday(order_date, label = TRUE, abbr = FALSE))

# Adding month column
retail <- retail %>%
  mutate(month = month(order_date, label = TRUE, abbr = TRUE))

# Summarizing to get total sales by day, month, week
total_sales_by_day <- retail %>%
  group_by(day_of_week) %>%
  summarize(total_sales = sum(sales), .groups = 'drop') %>%
  arrange(day_of_week)

total_sales_by_month <- retail %>%
  group_by(month) %>%
  summarize(total_sales = sum(sales), .groups = 'drop') %>%
  arrange(match(month, month.name)) 

# Bar plots
ggplot(total_sales_by_day, aes(x = day_of_week, y = total_sales, fill = day_of_week)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Sales by Day of the Week",
       x = "Day of the Week",
       y = "Total Sales") +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired")

ggplot(total_sales_by_month, aes(x = month, y = total_sales, fill = month)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Sales by Month of the Year",
       x = "Month of the Year",
       y = "Total Sales") +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired")
```
**Total Sales by Day of the Month**
```{r}
# Extract day of the month and month name
retail <- retail %>%
  mutate(day_of_month = day(order_date),
         month_name = month(order_date, label = TRUE, abbr = TRUE))  # abbr = TRUE for abbreviated month names

# Summarize
sales_by_day_month <- retail %>%
  group_by(month_name, day_of_month) %>%
  summarize(total_sales = sum(sales), .groups = 'drop') %>%
  arrange(month_name, day_of_month)

# Line plot with faceting for each month
ggplot(sales_by_day_month, aes(x = as.factor(day_of_month), y = total_sales, group = 1)) +
  geom_line(color = "dodgerblue") +
  facet_wrap(~month_name, scales = "free_y") +
  labs(title = "Total Sales by Day of the Month, by Month",
       x = "Day of the Month",
       y = "Total Sales") +
  theme_minimal()
```


## Weekly Aggregation
```{r}
# Group by year and week, and summarize sales
weekly_sales <- retail %>%
  mutate(week_year = as.Date(cut(order_date, "week"))) %>%
  group_by(week_year) %>%
  summarize(total_sales = sum(sales), .groups = 'drop')

# Create a zoo object
sales_zoo_weekly <- zoo(weekly_sales$total_sales, order.by = weekly_sales$week_year)
sales_ts_weekly <- ts(weekly_sales$total_sales, frequency=52)
```


**Plotting time series data vs time w/ Loess Regression line**
```{r}
# Convert zoo object to a data frame for ggplot
sales_data_frame <- data.frame(Date = index(sales_zoo_weekly), Sales = coredata(sales_zoo_weekly))

# Create an enhanced time series plot using ggplot2
ggplot(sales_data_frame, aes(x = Date, y = Sales)) +
  geom_line(color = "black") +  # Customize line color and thickness
  geom_smooth(method = "loess", color = "red2", se = FALSE, span = 0.1) + 
  labs(title = "Weekly Sales Over Time", x = "Date", y = "Total Sales") +
  theme_minimal() +  # Use a minimalistic theme
  theme(axis.title.x = element_text(face = "bold", color = "gray20"),  # Customize x-axis title
        axis.title.y = element_text(face = "bold", color = "gray20"))  # Customize y-axis title
```

* Perhaps some multiplicative behavior, though maybe not
* Definite seasonality

```{r}
autoplot(decompose(sales_ts_weekly))
```


**Checking for Normality**
```{r}
ggqqplot(sales_ts_weekly,
                    ylab = "Quantiles of Sales",
                    xlab = "Theoretical Quantiles",
                    ggtheme = theme_minimal(), 
                    color = "steelblue4", 
                    conf.int = TRUE,
                    title = "QQ Plot of Weekly Sales")

jb_test <- jarque.bera.test(sales_ts_weekly)
print(jb_test) # small p-value so data comes from non-normal distribution
```

**ACF and PACF plots**
```{r}
# significance level
N <- length(sales_ts_weekly)
sig_level <- 1.96 / sqrt(N)

# Exract acf and pacf data
acf_data <- acf(sales_ts_weekly, lag.max = 104, plot = FALSE)
pacf_data <- pacf(sales_ts_weekly, lag.max = 104, plot = FALSE)

# ACF Plot with significance lines
ggplot(data.frame(Lag = acf_data$lag[-1], ACF = acf_data$acf[-1]), aes(x = Lag, y = ACF)) +  # Exclude lag 0
  geom_bar(stat = "identity", fill = "steelblue", width = 0.01) + 
  geom_hline(yintercept = c(-sig_level, sig_level), linetype = "dashed", color = "darkred") +
  labs(title = "ACF", x = "Lag", y = "ACF") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())

# PACF Plot with significance lines
ggplot(data.frame(Lag = pacf_data$lag, PACF = pacf_data$acf), aes(x = Lag, y = PACF)) +
  geom_bar(stat = "identity", fill = "darkred", width = 0.01) + 
  geom_hline(yintercept = c(-sig_level, sig_level), linetype = "dashed", color = "darkblue") +
  labs(title = "PACF", x = "Lag", y = "PACf") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

$\text{\underline{Stationarity}}$

- Most tests indicate that the series is stationary, however the KPSS test indicates the series is *not* level stationary.
- 1st Differences t-test: Suggests that the series does not have a strong deterministic trend. Since the mean of the first differences is not significantly different from zero, it implies that any trend in the original series is likely stochastic rather than deterministic.

$\text{\underline{Seasonality}}$

- The ACF plot definitely indicates seasonality, at about 52 lags (52 weeks = 1 year)

$\text{\underline{ARMA Order}}$
- ACF suggests higher order MA (7 significant lags)
- PACF suggests maybe AR(2)

**Looking at mean of differences**
```{r}
mean(diff(sales_ts_weekly))
t.test(diff(sales_ts_weekly)) # cannot reject that the mean is actually 0
```

**KPSS and ADF Tests**
```{r}
# summary_table = summarize_arima_models(model1,model2, model3, model4, model5, model6)
# kable(table, format = "html", caption = "Manual Models") %>%
#   kable_classic(full_width = F, html_font = "Cambria")

run_stationarity_tests(sales_ts_weekly)
```


**Since there seems to be a stochastic trend, maybe differencing is appropriate**

## Looking at 2-Stage Differenced Timeseries
```{r}
two_diff_zoo = diff(diff(sales_zoo_weekly), 52)
two_diff_ts = diff(diff(sales_ts_weekly), 52)

# Convert zoo object to a data frame for ggplot
diff_data_frame <- data.frame(Date = index(two_diff_zoo), Sales = coredata(two_diff_zoo))

# Time series plot using ggplot2
ggplot(diff_data_frame, aes(x = Date, y = Sales)) +
  geom_line(color = "black") +
  geom_smooth(method = "loess", color = "red2", se = FALSE, span = 0.1) + 
  labs(title = "Seasonal Weekly Sales Differences", x = "Date", y = "Sales Seasonal Diffs") +
  theme_minimal() + 
  theme(axis.title.x = element_text(face = "bold", color = "gray20"),  
        axis.title.y = element_text(face = "bold", color = "gray20"))  

autoplot(decompose(two_diff_ts))

ggqqplot(two_diff_ts,
                    ylab = "Quantiles of Sales",
                    xlab = "Theoretical Quantiles",
                    ggtheme = theme_minimal(),  
                    color = "steelblue4", 
                    conf.int = TRUE,
                    title = "QQ Plot of Weekly Sales")

# significance level
N <- length(two_diff_ts)
sig_level <- 1.96 / sqrt(N)

# Exract acf and pacf data
acf_data <- acf(two_diff_ts, lag.max = 104, plot = FALSE)
pacf_data <- pacf(two_diff_ts, lag.max = 104, plot = FALSE)

# ACF Plot with significance lines
ggplot(data.frame(Lag = acf_data$lag[-1], ACF = acf_data$acf[-1]), aes(x = Lag, y = ACF)) +  # Exclude lag 0
  geom_bar(stat = "identity", fill = "steelblue", width = 0.01) + 
  geom_hline(yintercept = c(-sig_level, sig_level), linetype = "dashed", color = "darkred") +
  labs(title = "ACF", x = "Lag", y = "ACF") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())

# PACF Plot with significance lines
ggplot(data.frame(Lag = pacf_data$lag, PACF = pacf_data$acf), aes(x = Lag, y = PACF)) +
  geom_bar(stat = "identity", fill = "darkred", width = 0.01) + 
  geom_hline(yintercept = c(-sig_level, sig_level), linetype = "dashed", color = "darkblue") +
  labs(title = "PACF", x = "Lag", y = "PACf") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())

run_stationarity_tests(two_diff_ts)
```

```{r}
# Jarque-Bera test
jb_test <- jarque.bera.test(two_diff_ts)
print(jb_test) # Large p-value so data comes from normal distribution
```

```{r}
run_stationarity_tests(two_diff_ts)
```

$\text{\underline{Stationarity}}$

- Looks like there might be signs of overdifferencing
- Definitely stationary though
- Some cyclical patterns in ACF indicating seasonality, though the lags aren't significant


## Making SARIMA Models

Building Model Based off Previous Analysis:
```{r, fig.keep = 'none'}
model1 = Arima(sales_ts_weekly, order=c(0, 1, 1), seasonal=list(order=c(0, 1, 1), period=52))
summary(model1)
coeftest(model1)
Acf(model1$residuals, lag.max=52)
pacf(model1$residuals, lag.max=52)
Box.test(model1$residuals, type="L")
plot(forecast(model1, h=52))
```

Auto Arima Models:
```{r, fig.keep = 'none'}
auto_with_aic = auto.arima(sales_ts_weekly, ic='aic')
summary(auto_with_aic)
coeftest(auto_with_aic)
Acf(auto_with_aic$residuals, lag.max=52)
pacf(auto_with_aic$residuals, lag.max=52)
Box.test(auto_with_aic$residuals, type="L")
plot(forecast(auto_with_aic, h=52))
```

```{r, fig.keep = 'none'}
auto_with_bic = auto.arima(sales_ts_weekly, ic='bic')
print(auto_with_bic)
coeftest(auto_with_bic)
Acf(auto_with_bic$residuals, lag.max=52)
pacf(auto_with_bic$residuals, lag.max=52)
Box.test(auto_with_bic$residuals, type="L")
plot(forecast(auto_with_bic, h=52))
```
**auto.arima with Box Cox**
```{r, fig.keep = 'none'}
auto_with_aic = auto.arima(sales_ts_weekly, ic='aic', lambda="auto")
print(auto_with_aic)
coeftest(auto_with_aic)
Acf(auto_with_aic$residuals, lag.max=52)
pacf(auto_with_aic$residuals, lag.max=52)
Box.test(auto_with_aic$residuals, type="L")
plot(forecast(auto_with_aic, h=52))
```

```{r, fig.keep = 'none'}
auto_with_bic = auto.arima(sales_ts_weekly, ic='bic', lambda='auto')
print(auto_with_bic)
coeftest(auto_with_bic)
Acf(auto_with_bic$residuals, lag.max=52)
pacf(auto_with_bic$residuals, lag.max=52)
Box.test(auto_with_bic$residuals, type="L")
plot(forecast(auto_with_bic, h=52))
```

**Generating models with different parameter combinations**
```{r}
# Non-seasonal ARIMA orders
orders <- expand.grid(p = 0:2, d = 1, q = 0:2)

# Seasonal ARIMA orders
seasonal_orders <- expand.grid(P = 0:1, D = 0:1, Q = 0:1, s = 52)

# Initialize lists
model_list <- list()
problematic_models <- list()
```


```{r}
# Generate models with all combinations
for (i in 1:nrow(orders)) {
  for (j in 1:nrow(seasonal_orders)) {
    model_label <- paste("model", 
                         paste(orders[i, ], collapse = "_"), 
                         "x", 
                         paste(seasonal_orders[j, ], collapse = "_"), 
                         sep = "_")
    # tryCatch to handle errors
    result <- tryCatch({
      # Fit ARIMA model
      Arima(sales_ts_weekly,
            order = as.numeric(orders[i, 1:3]),
            seasonal = list(order = as.numeric(seasonal_orders[j, 1:3]),
                            period = as.integer(seasonal_orders[j, 4]))
      ) # Correctly close Arima function call
    }, 
    error = function(e) {
        # Handle error by returning NULL and logging the error
        cat(sprintf("Error in model %s: %s\n", model_label, e$message))
        return(NULL)
    })

    # Only store successful models
    if (!is.null(result)) {
      model_list[[model_label]] <- result
    } else {
      # Store problematic model configurations
      problematic_models[[model_label]] <- list(order = orders[i, ], seasonal_order = seasonal_orders[j, ])
    }
  }
}

```


**Best Models**
```{r, fig.keep = 'none'}
model1 = Arima(sales_ts_weekly, order=c(0, 1, 1), seasonal=list(order=c(0, 1, 1), period=52))
summary(model1)
coeftest(model1)
Acf(model1$residuals, lag.max=52)
pacf(model1$residuals, lag.max=52)
Box.test(model1$residuals, type="L")
plot(forecast(model1, h=52))
```

```{r, fig.keep = 'none'}
model2 = Arima(sales_ts_weekly, order=c(0, 1, 2), seasonal=list(order=c(0, 1, 1), period=52))
summary(model2)
coeftest(model2)
Acf(model2$residuals, lag.max=104)
pacf(model2$residuals, lag.max=104)
Box.test(model2$residuals, type="L")
plot(forecast(model2, h=104))
```


```{r}
model3 = Arima(sales_ts_weekly, order=c(1, 1, 2), seasonal=list(order=c(0, 1, 1), period=52))
summary(model3)
coeftest(model3)
Acf(model3$residuals, lag.max=104)
pacf(model3$residuals, lag.max=104)
plot(forecast(model3, h=104))
```

```{r}
model_new = Arima(sales_ts_weekly, order=c(5, 1, 1), seasonal=list(order=c(1, 1, 1), period=52))
summary(model_new)
coeftest(model_new)
Acf(model_new$residuals, lag.max=104)
pacf(model_new$residuals, lag.max=104)
plot(forecast(model_new, h=104))
```

**Including Box-Cox Tranforms**
```{r}
library("MASS")
```

```{r}
fit = lm(sales_ts_weekly ~ time(sales_ts_weekly))
plot(fit$residuals ~ fit$fitted.values)
plot(fit)
boxcox(fit)
```


```{r}
model4 = Arima(sales_ts_weekly, order=c(0, 1, 1), seasonal=list(order=c(0, 1, 1), period=52), lambda="auto")
summary(model4)
coeftest(model4)
Acf(model4$residuals, lag.max=104)
pacf(model4$residuals, lag.max=104)
plot(forecast(model4, h=104))
residuals <- residuals(model4)
Box.test(residuals, lag = 10, type = "Ljung-Box")
```

```{r}
model5 = Arima(sales_ts_weekly, order=c(0, 1, 2), seasonal=list(order=c(0, 1, 1), period=52), lambda="auto")
summary(model5)
coeftest(model5)
Acf(model5$residuals, lag.max=104)
pacf(model5$residuals, lag.max=104)
plot(forecast(model5, h=104))
residuals <- residuals(model5)
Box.test(residuals, lag = 10, type = "Ljung-Box")
```

```{r}
model6 = Arima(sales_ts_weekly, order=c(1, 1, 2), seasonal=list(order=c(0, 1, 1), period=52), lambda="auto")
summary(model6)
coeftest(model6)
Acf(model6$residuals, lag.max=104)
pacf(model6$residuals, lag.max=104)
plot(forecast(model6, h=104))
residuals <- residuals(model6)
Box.test(residuals, lag = 10, type = "Ljung-Box")
```

```{r}
model7 = Arima(sales_ts_weekly, order=c(5, 1, 1), seasonal=list(order=c(1, 1, 1), period=52), lambda="auto")
summary(model7)
coeftest(model7)
Acf(model7$residuals, lag.max=104)
pacf(model7$residuals, lag.max=104)
plot(forecast(model7, h=104))
residuals <- residuals(model7)
Box.test(residuals, lag = 10, type = "Ljung-Box")
```



```{r}
summary_table <- do.call(summarize_arima_models, model_list)

# Display the summary table using kable
kable(summary_table, format = "html", caption = "Summary of Expanded ARIMA Models") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```


```{r}
sorted_df <- summary_table[order(summary_table$AIC, summary_table$BIC),]

# Select the top 3 entries
top_three_models <- head(sorted_df, 3)

# Display the top three models
print(top_three_models)
```


Comparing Models
```{r}
summary_table = summarize_arima_models(model1, model2, model3, model_new)
kable(summary_table, format = "html", caption = "Best SARIMA Models") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

```{r}
summary_table <- mutate(summary_table, `Transform λ` = NA_real_)

model_descriptions <- c(
  "SARIMA(0,1,1)(0,1,1)[52] w/ λ",
  "SARIMA(0,1,2)(0,1,1)[52] w/ λ",
  "SARIMA(1,1,2)(0,1,1)[52] w/ λ",
  "SARIMA(5,1,1)(1,1,1)[52] w/ λ"
)

# Define new rows
new_data <- tibble(
  Num_Params = c(2, 3, 4, 8), 
  AIC = c(2736.82, 2736.85, 2736.82, 2739.93),
  BIC = c(2745.97, 2749.05, 2752.07, 2767.38),  
  Sigma2 = c(1908740, 1892540, 1850103, 1905153),  
  ACF1 = c(-0.08095574, 0.02305056, 0.02660522, 0.01637678),  
  Ljung_Box_pvalue = c(0.3207, 0.3293, 0.6162, 0.963),  
  `Transform λ` = rep(0.84, 4)
)

# Combine the model descriptions with the data
new_data$Model <- model_descriptions

# Convert existing summary_table row names to a column
if (is.null(summary_table$Model) && !is.null(rownames(summary_table))) {
  summary_table$Model <- rownames(summary_table)
}

# Append new data to the existing summary table
summary_table <- rbind(summary_table, new_data)


rownames(summary_table) <- summary_table$Model
summary_table$Model <- NULL  

kable(summary_table, format = "html", caption = "Best SARIMA Models") %>%
  kable_classic(full_width = F, html_font = "Cambria")

```


```{r}
str(summary_table)
```

```{r}
summary_table = summarize_arima_models(auto_with_aic, auto_with_bic)
kable(summary_table, format = "html", caption = "Auto.arima Models") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

```{r}
summary_table
```


### Backtesting

```{r}
# create validation set
ntest = 0.80*length(sales_ts_weekly)

pm1 = backtest(model4, sales_ts_weekly, orig=ntest, h=1)
pm2 = backtest(model5, sales_ts_weekly, orig=ntest, h=1)
pm3 = backtest(model6, sales_ts_weekly, orig=ntest, h=1)
pm4 = backtest(model7, sales_ts_weekly, orig=ntest, h=1)
```

```{r}
# Create a data frame with the backtesting results
backtest_results <- data.frame(
  Model = c("SARIMA(0,1,1)(0,1,1)[52]", 
            "SARIMA(0,1,2)(0,1,1)[52]", 
            "SARIMA(1,1,2)(0,1,1)[52]"),
  RMSE = c(7603.294, 7765.126, 7626.107),
  MAE = c(5801.433, 6060.102, 5953.322),
  MAPE = c(0.4926231, 0.5201279, 0.5174485),
  sMAPE = c(0.4039452, 0.4281201, 0.4123108)
)

kable(backtest_results, format = "html", caption = "Backtesting Results for SARIMA Models") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

```{r}
# Load necessary library
library(dplyr)

# Define the model names as previously described
model_names <- c(
  "SARIMA(0,1,1)(0,1,1)[52] w/ λ",
  "SARIMA(0,1,2)(0,1,1)[52] w/ λ",
  "SARIMA(1,1,2)(0,1,1)[52] w/ λ",
  "SARIMA(5,1,1)(1,1,1)[52] w/ λ"
)

# Define backtesting results
results <- data.frame(
  Model = model_names,
  RMSE = c(7603.294, 7765.126, 7626.107, 7743.23),
  MAE = c(5801.433, 6060.102, 5953.322, 6005.032),
  MAPE = c(0.4926231, 0.5201279, 0.5174485, 0.5115314),
  SMAPE = c(0.4039452, 0.4281201, 0.4123108, 0.4188037)
)

kable(results, format = "html", caption = "Backtesting Results for SARIMA Models") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```


### Looking at log sales

```{r}
# Convert zoo object to a data frame for ggplot
log_sales = log(sales_zoo_weekly)
log_sales_ts = log(sales_ts_weekly)
sales_data_frame <- data.frame(Date = index(log_sales), Sales = coredata(log_sales))

# Create an enhanced time series plot using ggplot2
ggplot(sales_data_frame, aes(x = Date, y = Sales)) +
  geom_line(color = "black") +  # Customize line color and thickness
  geom_smooth(method = "loess", color = "red2", se = FALSE, span = 0.08) + 
  labs(title = "Weekly Sales Over Time", x = "Date", y = "Total Sales") +
  theme_minimal() +  # Use a minimalistic theme
  theme(axis.title.x = element_text(face = "bold", color = "gray20"),  # Customize x-axis title
        axis.title.y = element_text(face = "bold", color = "gray20"))  # Customize y-axis title

autoplot(decompose(log_sales_ts))
```

Taking the log of the sales seems to over-correct for any multiplicative behavior in the data.

### Box-cox transformation

```{r}
library("MASS")
```

```{r}
fit = lm(sales_ts_weekly ~ time(sales_ts_weekly))
plot(fit$residuals ~ fit$fitted.values)
plot(fit)
boxcox(fit)
```

```{r}
lambda = 0.2
yBox = (sales_zoo_weekly^lambda-1)/lambda
autoplot(yBox)
fitBox = lm(yBox ~ time(sales_ts_weekly))
plot(fitBox)
plot(fitBox$residuals ~ fitBox$fitted.values)
```


```{r}
sales_data_frame <- data.frame(Date = index(yBox), Sales = coredata(yBox))

# Create an enhanced time series plot using ggplot2
ggplot(sales_data_frame, aes(x = Date, y = Sales)) +
  geom_line(color = "black") +  # Customize line color and thickness
  geom_smooth(method = "loess", color = "red2", se = FALSE, span = 0.08) + 
  labs(title = "Weekly Sales Over Time", x = "Date", y = "Total Sales") +
  theme_minimal() +  # Use a minimalistic theme
  theme(axis.title.x = element_text(face = "bold", color = "gray20"),  # Customize x-axis title
        axis.title.y = element_text(face = "bold", color = "gray20"))  # Customize y-axis title

autoplot(decompose(log_sales_ts))
```

```{r}
boxCox(fit, lambda = seq(-2, 2, by = 0.1))
```

